preprocessing

### 2022-11-14 r-prep/prep.Rmd
countries & kaya add

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  left_join(data_lulucf,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(
    EU = case_when(country %in% eurostat::eu_countries[2]$name~ TRUE, TRUE ~ FALSE),

  )

@@

data_kaya = data_base %>% 
  group_by(ISO,country,year,GDP_pc,pop) %>% 
  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
  left_join(data_iea,by=c("ISO","year")) %>%
  mutate(energy_intensity = energy/GDP_pc) %>%
  mutate(carbon_intensity = CO2/energy) %>%
  na.omit() %>% 
  pivot_longer(c(CO2,pop,GDP_pc,energy_intensity,carbon_intensity),names_to = "var",values_to = "value")

>>>>

data_base = data_gwp100 %>%
  left_join(data_wdi,by=c("ISO","year")) %>%
  left_join(data_lulucf,by=c("ISO","year")) %>%
  mutate(GHG_pc = GHG/pop) %>%
  mutate(GDP_pc = gdp_ppp/pop) %>%
  filter(year <= 2019) %>% 
  mutate(
    EU = country %in% eurostat::eu_countries[2]$name,
    woc = country != "China",
    deving_woc = woc & region_ar6_dev == "developing",
    deved = region_ar6_dev == "developed",
    adp_region_woc = woc & region_ar6_6 == "Asia and developing Pacific",
    adp_region_deving_woc = adp_region_woc & deving_woc
  ) %>% 
  select(-woc)

@@

data_kaya = data_base %>% 
  group_by(ISO,country,year,GDP_pc,pop,EU,deving_woc,deved,adp_region_woc,adp_region_deving_woc) %>% 
  summarise(CO2=sum(CO2,na.rm=TRUE)) %>%
  left_join(data_iea,by=c("ISO","year")) %>%
  mutate(energy_intensity = energy/GDP_pc) %>%
  mutate(carbon_intensity = CO2/energy) %>%
  na.omit() %>% 
  pivot_longer(c(CO2,pop,GDP_pc,energy_intensity,carbon_intensity),names_to = "var",values_to = "value")
